Do we need detailed demographic data to forecast plant population responses to climate change?

### 2016-07-11 manuscript/manuscript.Rmd
MEE submission version

## rmarkdown render options
output:
  pdf_document:
    fig_caption: true
    keep_tex: false
fontsize: 12pt
geometry: margin=1in
linkcolor: black
urlcolor: black

@@

\begin{enumerate}[label=\textbf{\arabic*}]
        \item Rapid environmental change has generated growing interest in forecasts of future population trajectories. Traditional population models built with detailed demographic observations from one study site can address the impacts of environmental change at particular locations, but are difficult to scale up to the landscape and regional scales relevant to management decisions.
        \item An alternative is to build models using population-level data which are much easier to collect than individual-level data over broad spatial scales.
However, it is unknown whether models built using population-level data adequately capture the effects of density-dependence and environmental forcing that are necessary to generate skillful forecasts.
        \item Here, we test the consequences of aggregating individual responses when forecasting the population states and trajectories of four perennial grass species in a semi-arid grassland in Montana, USA. We parameterized two population models for each species, one based on individual-level data (survival, growth and recruitment) and one on population-level data (percent cover), and compared their forecasting skill and forecast horizons with and without the inclusion of climate covariates. For both models we used Bayesian ridge regression to weight the influence of climate covariates for optimal prediction. 
        \item In the absence of climate effects, we found no significant difference between the forecasting skill of models based on individual-level data and models based on population-level data. Climate effects were weak, but increased forecasting skill for two species. Increases in skill with climate covariates were similar between model types.
        \item In our case study, percent cover models generated forecasts as skillful as those from a demographic model. For the goal of forecasting, models based on aggregated individual-level data may offer a practical alternative to data-intensive demographic models. Long time series of percent cover data already exist for many plant species. Modelers should exploit these data to predict the impacts of environmental change.
    \end{enumerate}

>>>>

## rmarkdown render options
output:
  pdf_document:
    fig_caption: true
    keep_tex: true
fontsize: 12pt
geometry: margin=1in
linkcolor: black
urlcolor: black

@@

\begin{enumerate}[label=\textbf{\arabic*}]
        \item Rapid environmental change has generated growing interest in forecasts of future population trajectories. Traditional population models built with detailed demographic observations from one study site can address the impacts of environmental change at particular locations, but are difficult to scale up to the landscape and regional scales relevant to management decisions. An alternative is to build models using population-level data which are much easier to collect than individual-level data over broad spatial scales. However, it is unknown whether models built using population-level data adequately capture the effects of density-dependence and environmental forcing that are necessary to generate skillful forecasts.
        \item Here, we test the consequences of aggregating individual responses when forecasting the population states and trajectories of four perennial grass species in a semi-arid grassland in Montana, USA. We parameterized two population models for each species, one based on individual-level data (survival, growth and recruitment) and one on population-level data (percent cover), and compared their forecasting skill and forecast horizons with and without the inclusion of climate covariates. For both models we used Bayesian ridge regression to weight the influence of climate covariates for optimal prediction. 
        \item In the absence of climate effects, we found no significant difference between the forecasting skill of models based on individual-level data and models based on population-level data. Climate effects were weak, but increased forecasting skill for two species. Increases in skill with climate covariates were similar between model types.
        \item In our case study, percent cover models generated forecasts as skillful as those from a demographic model. For the goal of forecasting, models based on aggregated individual-level data may offer a practical alternative to data-intensive demographic models. Long time series of percent cover data already exist for many plant species. Modelers should exploit these data to predict the impacts of environmental change.
    \end{enumerate}
